---
title: "Airplane Customer Satisfaction"
output: html_document
authors: Cosima, Nina and Viviane 
date: '2023-04-07'
---
Our Research Question: 

What aspects should the airline market to convince business travelers to upgrade from economy to business class? (Marketing-focused)

Rational:  

Increase profit for the airline. Business class was built to satisfy the need of business travelers. Business travelers make up to 75% of the annual airline profit because they are flying business or first class. On average the price of a business class ticket is four times the price of an economy ticket.  

Applied methods to answer our RQ: 

Which satisfaction variables do business class passengers rate significantly higher than economy class passengers? Select those with at least medium effect sizes. These are the aspects that should be marketed.

Question for the meeting:

1) Treat satisfaction variables as ordinal or interval? 

2) How can we add median/mean in our plot? + Labels 1-5 + remove NA

3) How can we merge (?) all the 6 plots?



Load all necessary packages
```{r}
library(tidyverse)
library(ggplot2)
library(effsize)
library(dplyr)
```


Read in the data 
```{r}

data <- read.csv("satisfaction_2015.csv", header = TRUE)
summary(data)
```


Clean the data: Remove all unnecessary columns and select only passengers that travel for business reasons. Remove class 'Eco Plus' so that we only have Eco and Business Class left. 
```{r}
data_clean <- data %>%  
  select(-c (id,Customer.Type,satisfaction_v2,Departure.Delay.in.Minutes,Arrival.Delay.in.Minutes))  
  
data_clean <- data_clean %>%  
  filter(Type.of.Travel == 'Business travel' & Class != 'Eco Plus')

data_clean[data_clean == 0] <- NA
view(data_clean)

#Class as factor + levels 
data_clean$Class <- factor(data_clean$Class)

class_levels <- levels(data_clean$Class)
```

We calculated the distributions and the effect sizes for each of the 14 variables. We also compared not only Business vs.Eco but also included Eco Plus. We found sig. differences between Eco and Eco Plus for a few variables. But due to the facts that the Eco Plus option is very limited in an Airplane and the differences for Eco vs. Business were more explicit than Eco Plus vs. Business we chose to limit our data to Eco and Business Class. We also had only a few passengers in the Eco Plus class. 

The following R blocks perform descriptive & interference statistical analyses and visualizations for 6 satisfaction variables. These are the variables with medium effect sizes and sig. group difference (Business > Eco). 


1) Seat Comfort Satisfaction Rating 

```{r}

# Meadian and mean for each group of 'class'

medians_seat.comfort <- aggregate(Seat.comfort ~ Class, data = data_clean, median)
medians_seat.comfort
print(medians_seat.comfort)

means_seat.comfort <- aggregate(Seat.comfort ~ Class, data = data_clean, mean)
means_seat.comfort

# Metric: T-Test 

results_t_1 <- t.test(Seat.comfort ~ Class , data = data_clean)
print(results_t_1)
##Calculate Effect size 
d_seatC <- cohen.d(data_clean$Seat.comfort ~ data_clean$Class, pooled = TRUE)
print(d_seatC)
### 0.54 medium

# Ordinal: perform Kruskal-Wallis test
kw <- kruskal.test(Seat.comfort ~ Class, data = data_clean)
kw
## Post-hoc tests using Dunn's test
install.packages('dunn.test')
library(dunn.test)
dunn <- dunn.test(data_clean$Seat.comfort, data_clean$Class, method = "holm")
dunn

# Visualization of the distribution 
## Convert satisfaction_ratings_for_comfort to a factor variable with ordered levels
data_clean$Seat.comfort <- factor(data_clean$Seat.comfort, levels = 1:5, ordered = TRUE)

## Group data by Class and satisfaction_ratings_for_comfort, and calculate proportions
data_grouped <- data_clean %>%
  group_by(Class, Seat.comfort) %>%
  summarize(Count = n()) %>%
  mutate(Proportion = Count / sum(Count))

## Create stacked bar chart with ggplot2
ggplot(data_grouped, aes(x = Class, y = Proportion, fill = Seat.comfort, desc_stat = 'median')) +
  geom_col(position = "fill") +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(x = "Class", y = "Proportion", fill = "Satisfaction Ratings for Seat Comfort")
```

2) Online Boarding Satisfaction Rating 

```{r}

# Meadian and mean for each group of 'class'
medians_online_boarding <- aggregate(Online.boarding ~ Class, data = data_clean, median)
medians_online_boarding 

means_online_boarding  <- aggregate(Online.boarding   ~ Class, data = data_clean, mean)
means_online_boarding

# Metric: T Test 
results_t_2 <- t.test(Online.boarding ~ Class , data = data_clean)
print(results_t_2)
## Calculate Effect size 
d_Oboarding <- cohen.d(data_clean$Online.boarding~ data_clean$Class, pooled = TRUE)
print(d_oboarding)
### 0.71 medium

# ordinal: perform Kruskal-Wallis test
kw <- kruskal.test(Online.boarding  ~ Class, data = data_clean)
kw
##Post-hoc tests using Dunn's test
dunn <- dunn.test(data_clean$Online.boarding, data_clean$Class, method = "holm")
dunn

# Visualization of the distribution 
```

3) On board Service Satisfaction Ratings 

```{r}
# Meadian and mean for each group of 'class'
medians_board_service <- aggregate(On.board.service ~ Class, data = data_clean, median)
medians_board_service

means_board_service<- aggregate(On.board.service  ~ Class, data = data_clean, mean)
means_board_service

# Metric: T Test 
results_t_3 <- t.test(On.board.service ~ Class , data = data_clean)
print(results_t_3)
## Calculate Effect size 
d_Oservice <- cohen.d(data_clean$On.board.service~ data_clean$Class, pooled = TRUE)
print(d_Oservice)
###0.65 medium

# Oridanl: Perform Kruskal-Wallis test
kw <- kruskal.test(On.board.service  ~ Class, data = data_clean)
kw
##Post-hoc tests using Dunn's test
dunn <- dunn.test(data_clean$On.board.service , data_clean$Class, method = "holm")
dunn

# Visualization of the distribution 
```

4) Baggage handling Satisfaction Ratings 

```{r}
# Meadian and mean for each group of 'class'
medians_baggage <- aggregate(Baggage.handling ~ Class, data = data_clean, median)
medians_baggage

means_baggage <- aggregate(Baggage.handling ~ Class, data = data_clean, mean)
means_baggage

# Metric: T Test 
results_t_4 <- t.test(Baggage.handling  ~ Class , data = data_clean)
print(results_t_4)
##Calculate Effect size 
d_baggage <- cohen.d(data_clean$Baggage.handling ~ data_clean$Class, pooled = TRUE)
print(d_baggage)
### 0.54 medium

# Ordinal: Perform Kruskal-Wallis test
kw <- kruskal.test(Baggage.handling ~ Class, data = data_clean)
kw
## Post-hoc tests using Dunn's test
dunn <- dunn.test(data_clean$Baggage.handling , data_clean$Class, method = "holm")
dunn

# Visualization of the distribution 
```

5) Check-In Service Satisfaction Ratings 

```{r}
# Meadian and mean for each group of 'class'
medians_checkin <- aggregate(Checkin.service ~ Class, data = data_clean, median)
medians_checkin

means_checkin <- aggregate(Checkin.service ~ Class, data = data_clean, mean)
means_checkin

# Metric:  T Test
results_t_5 <- t.test(Checkin.service  ~ Class , data = data_clean)
print(results_t_5)
## Calculate Effect size 
d_checkIn <- cohen.d(data_clean$Checkin.service ~ data_clean$Class, pooled = TRUE)
print(d_checkIn)
### 0.56 medium
# Ordinal: Perform Kruskal-Wallis test
kw <- kruskal.test(Checkin.service ~ Class, data = data_clean)
kw
## Post-hoc tests using Dunn's test
dunn <- dunn.test(data_clean$Checkin.service, data_clean$Class, method = "holm")
dunn

# Visualization of the distribution 
```

6) In-flight Service Satisfaction Ratings 

```{r}
# Meadian and mean for each group of 'class'
medians_inflight_service <- aggregate(Inflight.service ~ Class, data = data_clean, median)
medians_inflight_service

means_inflight_service <- aggregate(Inflight.service ~ Class, data = data_clean, mean)
means_inflight_service

# Metric: T Test 
results_t_6 <- t.test(Inflight.service ~ Class , data = data_clean)
print(results_t_6)
## Calculate Effect size 
d_flightSer<- cohen.d(data_clean$Inflight.service ~ data_clean$Class, pooled = TRUE)
print(d_flightSer)
### 0.54 medium

# Ordinal: Perform Kruskal-Wallis test
kw <- kruskal.test(Inflight.service~ Class, data = data_clean)
kw
## Post-hoc tests using Dunn's test
dunn <- dunn.test(data_clean$Inflight.service, data_clean$Class, method = "holm")
dunn

# Visualization of the distribution 
```